---
title: "Historic OX-I Quality"
output: html_notebook
---

Estimate changes in performance of machines over time by looking at OX-I data.

Check especially for bulb tests.

Get OX-I rec nums from standards.

Find all samples with those rec nums in os or no_os.

Need data on target size, counts, etc.

Work with un-blank corrected data preferentially.

# Finding data

Data more recent than 2002 seems pretty straightforward, other than some odd gf_date's that put CFAMS data in the 1990's. Older data is more problematic. Looking into it.

## Old data



```{r}
library(amstools)
library(tidyverse)
library(DBI)
library(skimr)
```
```{r}
db <- conNOSAMS()
no_os <- tbl(db, "no_os")
os <- tbl(db, "os")
standards <- tbl(db, "standards")
target <- tbl(db, "target")
graphite <- tbl(db, "graphite")
wheel_pos <- tbl(db, "wheel_pos")
ams_results <- tbl(db, "ams_results")
dbListFields(db, "archive")
dbListTables(db)

head(ams_results)

old_ox <- ams_results %>% 
  inner_join(target) %>% 
  inner_join(graphite) %>% 
  inner_join(standards)

ox_target <- target %>% 
  filter(target_name %like% "X%") %>% 
  select(tp_num, target_name, tp_date_pressed, osg_num) %>% 
  inner_join(graphite) %>% 
  inner_join(no_os) %>% 
  arrange(tp_date_pressed)

head(ox_target)
head(no_os)

ox <- no_os %>% 
  select(tp_num, f_modern, f_int_error, f_ext_error, primary_std, q_flag) %>% 
  inner_join(select(target, tp_num, tp_date_pressed, osg_num, 
                    rec_num, graphite_lab, min_time)) %>% 
  inner_join(select(wheel_pos, wheel_id, tp_num)) %>% 
  inner_join(select(graphite, osg_num, gf_date, gf_date_to_ams, 
                    gf_start_time, gf_co2_qty, gf_devel, gf_test)) %>% 
  inner_join(select(standards, rec_num, sample_id, Fm_cons)) %>% 
  collect() %>% 
  filter(str_detect(sample_id, "^[ ]?OX-?[I1][ \\/]") | rec_num == 34148) %>% 
  mutate(rec_num = as.factor(rec_num),
         system = as.factor(ifelse(str_detect(wheel_id, "^CFAMS"), "CFAMS", "USAMS")))

str(ox)
skim(ox)
```

```{r}
ox %>% 
  filter(f_modern > 0.9,
         f_modern < 1.2) %>% 
ggplot(aes(tp_date_pressed, f_modern, color = system)) +
  geom_point() +
  ylim(0.9, 1.2)
```

Looks like there were CFAMS wheels back in the 1990's? Problems with gf_date.
```{r}
ox %>% 
  filter(gf_date < "2000-01-01",
         system == "CFAMS") %>% 
  group_by(wheel_id)
```

```{r}
ox %>% 
  filter(f_modern > 0.9,
         f_modern < 1.2) %>% 
  ggplot(aes(factor(rec_num), f_modern)) +
           geom_boxplot()
```

